README

### 2016-12-11 src/README.Rmd
Knit .md files, remove extra file

---
title: "Journal Article Sampling Methodology"
output: github_document
---

@@

journal_list[1:20, -4] # drop h-index median value just to tidy things up.

journal_list[1:10, ] # select the top ten journals in plant pathology only
```

@@

```{r journal_sample_order}
journals <- as.data.frame(sample(1:10, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

@@

journals[1:100, -1]
```

>>>>

---
title: "README"
output: github_document
---

@@

journal_list[1:20, -4] # drop h-index median value
```

@@

```{r journal_sample_order}
journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

@@

journals[1:100, -1]

```

### Check the number of articles per journal

```{r}
journals %>%  
 group_by(Publication) %>% 
    tally(sort = TRUE)

```
